Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure

### 2020-07-14 CCIAQVTS/CCIAQVTS.tex
made the hyphens consistent whereever PRA was consistent (PRA inconsistent about quantum-accessible, non-existence, non-zero, etc.

    The Triangle structure (\cref{fig:triangle_structure}) is a causal structure comprised of three parties labeled $A, B,$ and $C$ arranged in a triangular configuration while pairwise sharing hidden (latent) variables $X, Y,$ and $Z$. It has been extensively studied previously (see, e.g.,~\cite[Fig. 1]{Steudel_2010},~\cite[Fig. 6]{Chaves_2014},~\cite[Fig. 8]{Branciard_2012},~\cite[Fig. 8, App. E]{Henson_2014},~\cite[Fig. 3]{Fritz_2012},~\cite[Fig. 4]{Weilenmann_2016}, and~\cite[Fig. 1]{Inflation}). An overview of some milestone results is provided in \cref{sec:triangle_structure}. Identifying causal compatibility inequalities for this configuration has been seen as particularly challenging~\cite{Branciard_2012}. Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out-of-reach for the Triangle structure.

    This work finds causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions. This accomplishment was made possible through the combination of two previous developments: first, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure, and second, the framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}. Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer insights into quantum nonclassicality \cite{Navascues_2017}. Moreover, these inequalities offer an avenue for recognizing previously unknown forms of nonclassicality. The authors' attempts to find such novel resources were met with only partial success, suggesting the need for both conceptual refinements and future exploration.

@@

    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:compatibility_as_factorization}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}. The conditional distributions in \cref{eq:compatibility_as_factorization} (i.e. $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}. If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$. When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is possible to completely determine whether or not $\prob[\nodes]$ is compatible with $\graph$ by computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}. A challenge, however, is presented when one is supplied with a partial observation, i.e. a joint distribution $\prob[\nodes_{O}]$ where $\nodes_{O} \subset \nodes$ is some subset of variables referred to as the \term{observable nodes} $\nodes_O$. In such cases, $\prob[\nodes_{O}]$ does not induce a unique set of causal parameters for $\graph$ and \cref{eq:compatibility_as_factorization} can not be verified by direction calculation. Instead, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \sum_{n \not \in \nodes_{O}} \prob[\nodes]$ where $\prob[\nodes]$ is again given by \cref{eq:compatibility_as_factorization}. The complementary, unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$, and should be understood as hidden random variables that are unknowable either by some fundamental process or cannot be measured due to other limitations.

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two common approaches worth mentioning here. The first is to recognize that many equality constraints are implied by the causal structure, including conditional independence relations and so-called Verma constraints among others; see Refs. \cite{evans2015margins,evans2017markov} for thorough treatments. The failure to satisfy an equality constraint immediately disqualifies $\prob[\nodes_{O}]$ from being compatible with $\graph$. Equality constraints are easily derived given a causal structure, and checking equality-constraints satisfaction is the minimalistic algorithm which powers the overwhelming majority of practical causal inference hypothesis testing in the fields of machine learning and artificial intelligence. In quantum theory, however, we require strong, more sensitive, causal inference techniques. This is because the equality constraints satisfied by compatible classical correlations are also all satisfied by quantum correlations \cite{Henson_2014}.
    Our focus, therefore, in on deriving \emph{inequality} constraints (over $\prob[\nodes_{O}]$ and its marginals) implied by a causal structure, which we term \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}. For some causal structures, the equality constraints associated with it are sufficient to perfectly characterize the distributions genuinely compatible with it; for others, however, inequality constraints are also important. Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell structure, and the Triangle structure studied here, among infinitely many others.
    Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:inflation_technique_summary} discusses the Inflation Technique as applied in this work.

@@

    From the perspective of identifying quantum nonclassicality, a causal structure $\graph$ adopts the role of a classical hypothesis. Therefore, nonclassicality becomes synonymous with incompatibility: if a distribution $\prob[\nodes_{O}]$ is incompatible, then it is nonclassical. Henceforth, we will use these two terms interchangeably. From a resource standpoint, if the nonclassicality of $\prob[\nodes_{O}]$ with $\graph$ can be witnessed by an inequality $I$, but nevertheless $\prob[\nodes_{O}]$ can be implemented using quantum states and measurements while otherwise respecting the causal relations of $\graph$, then the causal compatibility inequality $I$ represents a task or game where quantum resources out-perform classical resources relative to $\graph$.

@@

    Let us now contrast the classical definition of compatibility with its quantum generalization. Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems. Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement sets $M_{A|S_A}, M_{B|S_B}$\footnote{Note that a measurement set $M_{A} = \bc{M_{A}^{1}, M_{A}^{2}, \ldots, M_{A}^{k}}$ services a shorthand notation in the following sense, $\prob[A] = \Tr\bs{\rho M_{A}} \implies \prob[A]\br{a} = \Tr\bs{\rho M_{A}^{a}}$.} with indices conditional upon the measurement settings, such that
    \begin{align}\label{eq:bellQcompat}
    \prob[AB|S_AS_B] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
    \end{align}
    The nonclassicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions. A notable example is the Clauser-Horne-Shimony-Holt (CHSH) inequality~\cite{CHSH_Original}.
    \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the nonclassical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type. Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.

@@

    As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.

@@

    The Triangle structure serves as an excellent test case for furthering our understanding of quantum nonclassicality in network causal structures. It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
    For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \cite{Fritz_2012,Inflation}, unlike for the Bell structure. The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so it is known to possess quantum nonclassicality. It seems reasonable to assume that quantum nonclassicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicality are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of nonclassicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure. In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is nonclassical, it is also non-quantum. The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. \Cref{sec:preliminary_research} reports our attempt to utilize these aforementioned inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit nonclassical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum nonclassicality and prompts the discovery of \textit{new} inequalities.

    \section{Fritz Distribution}
    \label{sec:fritz_distribution}
    \begin{figure}
    \begin{nscenter}
        \scalebox{1.0}{\includegraphics{figure_triangle_structure_operational_fritz_bell.pdf}}
        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
        \label{fig:triangle_structure_with_fritz_bell_embedded}
    \end{nscenter}
    \end{figure}

@@

    In~\cref{eq:fritz_dist_bit_variant}, the notation $\prob[\fritz][a_{l}a_{r},b_{l}b_{r},c_{l}c_{r}] = \prob[][A_{l}\mapsto a_{l},A_{r}\mapsto a_{r},B_{l}\mapsto b_{l},B_{r}\mapsto b_{r},C_{l}\mapsto c_{l},C_{r}\mapsto c_{r}]$ is used as shorthand. This observation can be difficult to verify using~\cref{eq:fritz_dist_bit_variant}, but becomes easier after organizing the possible outcomes into a $4 \times 4 \times 4$ grid as depicted in \cref{fig:fritz_distribution_visualized}. From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $A,B$ into a $2 \times 2$ block. Effectively, $C$'s bits are perfectly correlated with the left-bits of $A,B$; $C_l = A_l$ and $C_r = B_l$.

@@

            \caption{The Fritz distribution visualized using a $4 \times 4 \times 4$ grid. The $4$ outcomes of $A,B,C$ are written in binary as a doublet of bits to illustrate that certain bits act as measurement pseudo-settings.}

@@

    As an example, the famous CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original} is translated into a constraint on the correlation between the right-bits of $A$ and $B$ under~\cref{eq:fritz_relabelling},

@@

    It is important to understand the domain in which Fritz's proof of incompatibility is valid; its proof relies on the perfect correlation between $C$'s outcomes and the measurement pseudo-settings (left-bits) of $A$ and $B$. For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can be said with confidence regarding if the resulting modified distribution is classical or not? At what point does the resulting distribution transition from incompatibility to compatibility? This question is partially answered in \cref{sec:noise}.

@@

    Explicitly, we parameterized the subset of quantum distributions accessible by bipartite qubit density matrices and $2$-outcome POVM measurements\footnote{In \cref{sec:optimizations}, we discuss methods for conducting similar parameterizations of quantum states and measurements.}. This preliminary investigation did not yield interesting solutions, as none of the Triangle structure inequalities in~\cite{Inflation} or~\cite{Henson_2014} were violated\footnote{We also directly checked all 2-outcome coarse-grainings of the Fritz distribution against the inequalities in~\cite{Inflation,Henson_2014}, with no violation.}. Unfortunately, these early results are inconclusive for two reasons. First, an exhaustive search would need to consider the possibility of larger Hilbert spaces for the shared quantum states. Second, it is known that the inequalities~\cite{Inflation} are incomplete; there exists other constraints on two outcome distributions for the Triangle structure yet to be discovered.

    Nonetheless, having failed to observe a quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for \emph{non}-classical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.

@@

    The Inflation Technique is known to completely solve the causal compatibility problem through increasing orders of inflations~\cite{Navascues_2017}. Consequently, the derivation of \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality} is guaranteed by~\cite{Navascues_2017} for sufficiently large inflations. Nonetheless, the following inequalities were obtained using the relatively small inflations found in \cref{fig:inflations}\footnote{Note that the adjectives \textit{large} and \textit{small} used to describe an inflation only become well-defined in the context of the hierarchy proposed in~\cite{Navascues_2017}. For example, the Web Inflation in \cref{fig:the_web_inflation} is second in the hierarchy of~\cite{Navascues_2017} whereas the Wagon-Wheel Inflation in \cref{fig:wagon_wheel_inflation} is somewhere between the first and second order.}. This efficiency is not universally guaranteed; for comparison, we remark that unlike the Fritz distribution, the conjectured incompatibility of the $4$-outcome distribution proposed by \cite{Gisin_2017} is \textit{not} confirmed by Inflation Technique at the same level.

@@

    \Cref{eq:ww_ineq} is termed the Wagon-Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}. Moreover, note that \Cref{eq:ww_ineq} is reported using the same two-bit notation discussed in~\cref{sec:fritz_distribution} such that $\prob[A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}][a_{l}a_{r}b_{l}b_{r}c_{l}c_{r}] = \prob[ABC][abc]$.

@@

    In order for the numerical optimization to avoid distributions similar to $\prob[\fritz]$ we require an objective function which is \emph{not} tailor-designed to witness $\prob[\fritz]$. Finding such an inequality proved extremely challenging; while we could generate thousands of inequalities using the Inflation Technique~\cite{Inflation}, it appeared than only a vanishingly-small fraction of those inequalities admitted quantum violation whatsoever. We therefore modified the Inflation Technique to give us an inequality which both witnesses the nonclassicality of $\prob[\fritz]$ but which is also symmetric with respect to any permutation of the variables $A, B, C$, resulting in \cref{eq:symmetric_web_inequality}. The modification of the Inflation Techniques which forces symmetry is explained in \cref{sec:symmetric_inequalities}. As $\prob[\fritz]$ is strongly asymmetric due to the special role of $C$, we can hope that a symmetric inequality (even one which does witness $\prob[\fritz]$) might achieve its \emph{optimal} quantum violation on a distribution qualitative distinct from $\prob[\fritz]$. The details of our numerical finding are discussed in \cref{sec:optimizations}.

@@

    Since the inequalities we seek to optimally violate are polynomial, and since the space of quantum-accessible distributions is non-convex, we employ a number of optimization methods consecutively in an attempt to avoid pitfalls associated identifying local minima and ill-conditioned convergence. Specifically, the Broyden-Fletcher-Goldfarb-Shanno method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.

>>>>

    The Triangle structure (\cref{fig:triangle_structure}) is a causal structure comprised of three parties labeled $A, B,$ and $C$ arranged in a triangular configuration while pairwise sharing hidden (latent) variables $X, Y,$ and $Z$. It has been extensively studied previously (see, e.g.,~\cite[Fig. 1]{Steudel_2010},~\cite[Fig. 6]{Chaves_2014},~\cite[Fig. 8]{Branciard_2012},~\cite[Fig. 8, App. E]{Henson_2014},~\cite[Fig. 3]{Fritz_2012},~\cite[Fig. 4]{Weilenmann_2016}, and~\cite[Fig. 1]{Inflation}). An overview of some milestone results is provided in \cref{sec:triangle_structure}. Identifying causal compatibility inequalities for this configuration has been seen as particularly challenging~\cite{Branciard_2012}. Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out of reach for the Triangle structure.

    This work finds causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions. This accomplishment was made possible through the combination of two previous developments: first, the insight of \citet{Fritz_2012} regarding the ability to reinterpret the Bell structure as a portion of the Triangle structure, and second, the framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}. Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer insights into quantum nonclassicality \cite{Navascues_2017}. Moreover, these inequalities offer an avenue for recognizing previously unknown forms of nonclassicality. The authors' attempts to find such novel resources were met with only partial success, suggesting the need for both conceptual refinements and future exploration.

@@

    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:compatibility_as_factorization}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}. The conditional distributions in \cref{eq:compatibility_as_factorization} (i.e. $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}. If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$. When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is possible to completely determine whether or not $\prob[\nodes]$ is compatible with $\graph$ by computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}. A challenge, however, is presented when one is supplied with a partial observation, i.e. a joint distribution $\prob[\nodes_{O}]$ where $\nodes_{O} \subset \nodes$ is some subset of variables referred to as the \term{observable nodes} $\nodes_O$. In such cases, $\prob[\nodes_{O}]$ does not induce a unique set of causal parameters for $\graph$ and \cref{eq:compatibility_as_factorization} can not be verified by direction calculation. Instead, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or nonexistence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \sum_{n \not \in \nodes_{O}} \prob[\nodes]$ where $\prob[\nodes]$ is again given by \cref{eq:compatibility_as_factorization}. The complementary, unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$, and should be understood as hidden random variables that are unknowable either by some fundamental process or cannot be measured due to other limitations.

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two common approaches worth mentioning here. The first is to recognize that many equality constraints are implied by the causal structure, including conditional independence relations and so-called Verma constraints among others; see Refs. \cite{evans2015margins,evans2017markov} for thorough treatments. The failure to satisfy an equality constraint immediately disqualifies $\prob[\nodes_{O}]$ from being compatible with $\graph$. Equality constraints are easily derived given a causal structure, and checking equality-constraint satisfaction is the minimalistic algorithm which powers the overwhelming majority of practical causal inference hypothesis testing in the fields of machine learning and artificial intelligence. In quantum theory, however, we require strong, more sensitive, causal inference techniques. This is because the equality constraints satisfied by compatible classical correlations are also all satisfied by quantum correlations \cite{Henson_2014}.
    Our focus, therefore, in on deriving \emph{inequality} constraints (over $\prob[\nodes_{O}]$ and its marginals) implied by a causal structure, which we term \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}. For some causal structures, the equality constraints associated with it are sufficient to perfectly characterize the distributions genuinely compatible with it; for others, however, inequality constraints are also important. Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell structure, and the Triangle structure studied here, among infinitely many others.
    Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:inflation_technique_summary} discusses the Inflation Technique as applied in this work.

@@

    From the perspective of identifying quantum nonclassicality, a causal structure $\graph$ adopts the role of a classical hypothesis. Therefore, nonclassicality becomes synonymous with incompatibility: if a distribution $\prob[\nodes_{O}]$ is incompatible, then it is nonclassical. Henceforth, we will use these two terms interchangeably. From a resource standpoint, if the nonclassicality of $\prob[\nodes_{O}]$ with $\graph$ can be witnessed by an inequality $I$, but nevertheless $\prob[\nodes_{O}]$ can be implemented using quantum states and measurements while otherwise respecting the causal relations of $\graph$, then the causal compatibility inequality $I$ represents a task or game where quantum resources outperform classical resources relative to $\graph$.

@@

    Let us now contrast the classical definition of compatibility with its quantum generalization. Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems. Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement sets $M_{A|S_A}, M_{B|S_B}$\footnote{Note that a measurement set $M_{A} = \bc{M_{A}^{1}, M_{A}^{2}, \ldots, M_{A}^{k}}$ services a shorthand notation in the following sense, $\prob[A] = \Tr\bs{\rho M_{A}} \implies \prob[A]\br{a} = \Tr\bs{\rho M_{A}^{a}}$.} with indices conditional upon the measurement settings, such that
    \begin{align}\label{eq:bellQcompat}
    \prob[AB|S_AS_B] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
    \end{align}
    The nonclassicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions. A notable example is the Clauser-Horne-Shimony-Holt (CHSH) inequality~\cite{CHSH_Original}.
    \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
    Nontrivial Bell inequalities such as the CHSH inequality are capable of witnessing the nonclassical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type. Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.

@@

    As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pairwise sharing latent variables $X, Y, Z$.

@@

    The Triangle structure serves as an excellent test case for furthering our understanding of quantum nonclassicality in network causal structures. It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
    For example, the spaces of both classical and quantum distributions on the Triangle structure are nonconvex \cite{Fritz_2012,Inflation}, unlike for the Bell structure. The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible but quantum distribution for the Triangle structure, so it is known to possess quantum nonclassicality. It seems reasonable to assume that quantum nonclassicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicality are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of nonclassicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure. In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is nonclassical, it is also nonquantum. The nonquantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. \Cref{sec:preliminary_research} reports our attempt to utilize these aforementioned inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit nonclassical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum nonclassicality and prompts the discovery of \textit{new} inequalities.

    \section{Fritz Distribution}
    \label{sec:fritz_distribution}
    \begin{figure}
    \begin{nscenter}
        \scalebox{1.0}{\includegraphics{figure_triangle_structure_operational_fritz_bell.pdf}}
        \caption{The Triangle structure reimagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
        \label{fig:triangle_structure_with_fritz_bell_embedded}
    \end{nscenter}
    \end{figure}

@@

    In~\cref{eq:fritz_dist_bit_variant}, the notation $\prob[\fritz][a_{l}a_{r},b_{l}b_{r},c_{l}c_{r}] = \prob[][A_{l}\mapsto a_{l},A_{r}\mapsto a_{r},B_{l}\mapsto b_{l},B_{r}\mapsto b_{r},C_{l}\mapsto c_{l},C_{r}\mapsto c_{r}]$ is used as shorthand. This observation can be difficult to verify using~\cref{eq:fritz_dist_bit_variant}, but becomes easier after organizing the possible outcomes into a $4 \times 4 \times 4$ grid as depicted in \cref{fig:fritz_distribution_visualized}. From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $A,B$ into a $2 \times 2$ block. Effectively, $C$'s bits are perfectly correlated with the left-hand bits of $A,B$; $C_l = A_l$ and $C_r = B_l$.

@@

            \caption{The Fritz distribution visualized using a $4 \times 4 \times 4$ grid. The $4$ outcomes of $A,B,C$ are written in binary as a doublet of bits to illustrate that certain bits act as measurement pseudosettings.}

@@

    As an example, the famous CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original} is translated into a constraint on the correlation between the right-hand bits of $A$ and $B$ under~\cref{eq:fritz_relabelling},

@@

    It is important to understand the domain in which Fritz's proof of incompatibility is valid; its proof relies on the perfect correlation between $C$'s outcomes and the measurement pseudosettings (left-hand bits) of $A$ and $B$. For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can be said with confidence regarding if the resulting modified distribution is classical or not? At what point does the resulting distribution transition from incompatibility to compatibility? This question is partially answered in \cref{sec:noise}.

@@

    Explicitly, we parameterized the subset of quantum distributions accessible by bipartite qubit density matrices and two-outcome POVM measurements\footnote{In \cref{sec:optimizations}, we discuss methods for conducting similar parameterizations of quantum states and measurements.}. This preliminary investigation did not yield interesting solutions, as none of the Triangle structure inequalities in~\cite{Inflation} or~\cite{Henson_2014} were violated\footnote{We also directly checked all two-outcome coarse grainings of the Fritz distribution against the inequalities in~\cite{Inflation,Henson_2014}, with no violation.}. Unfortunately, these early results are inconclusive for two reasons. First, an exhaustive search would need to consider the possibility of larger Hilbert spaces for the shared quantum states. Second, it is known that the inequalities~\cite{Inflation} are incomplete; there exists other constraints on two outcome distributions for the Triangle structure yet to be discovered.

    Nonetheless, having failed to observe a quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for nonclassical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.

@@

    The Inflation Technique is known to completely solve the causal compatibility problem through increasing orders of inflations~\cite{Navascues_2017}. Consequently, the derivation of \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality} is guaranteed by~\cite{Navascues_2017} for sufficiently large inflations. Nonetheless, the following inequalities were obtained using the relatively small inflations found in \cref{fig:inflations}\footnote{Note that the adjectives \textit{large} and \textit{small} used to describe an inflation only become well defined in the context of the hierarchy proposed in~\cite{Navascues_2017}. For example, the Web Inflation in \cref{fig:the_web_inflation} is second in the hierarchy of~\cite{Navascues_2017} whereas the Wagon-Wheel Inflation in \cref{fig:wagon_wheel_inflation} is somewhere between the first and second order.}. This efficiency is not universally guaranteed; for comparison, we remark that unlike the Fritz distribution, the conjectured incompatibility of the four-outcome distribution proposed by \cite{Gisin_2017} is \textit{not} confirmed by Inflation Technique at the same level.

@@

    \Cref{eq:ww_ineq} is termed the Wagon-Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}. Moreover, note that \Cref{eq:ww_ineq} is reported using the same two-bit notation discussed in~\cref{sec:fritz_distribution} such that $\prob[A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}][a_{l}a_{r}b_{l}b_{r}c_{l}c_{r}] = \prob[ABC][abc]$.

@@

    In order for the numerical optimization to avoid distributions similar to $\prob[\fritz]$ we require an objective function which is \emph{not} tailor designed to witness $\prob[\fritz]$. Finding such an inequality proved extremely challenging; while we could generate thousands of inequalities using the Inflation Technique~\cite{Inflation}, it appeared than only a vanishingly small fraction of those inequalities admitted quantum violation whatsoever. We therefore modified the Inflation Technique to give us an inequality which both witnesses the nonclassicality of $\prob[\fritz]$ but which is also symmetric with respect to any permutation of the variables $A, B, C$, resulting in \cref{eq:symmetric_web_inequality}. The modification of the Inflation Techniques which forces symmetry is explained in \cref{sec:symmetric_inequalities}. As $\prob[\fritz]$ is strongly asymmetric due to the special role of $C$, we can hope that a symmetric inequality (even one which does witness $\prob[\fritz]$) might achieve its \emph{optimal} quantum violation on a distribution qualitative distinct from $\prob[\fritz]$. The details of our numerical finding are discussed in \cref{sec:optimizations}.

@@

    Since the inequalities we seek to optimally violate are polynomial, and since the space of quantum-accessible distributions is nonconvex, we employ a number of optimization methods consecutively in an attempt to avoid pitfalls associated identifying local minima and ill-conditioned convergence. Specifically, the Broyden-Fletcher-Goldfarb-Shanno method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient-descent-based methods.
